An Invariant Framework for Conducting Reproducible Computational Science

### 2015-01-12 evolution.tex
Major cleanup

\section{Evolving the Artifact}

It is clear that the artifact, as provided, is not in a suitable form
for preservation.  While it might be technically possible to automatically
capture the entire virtual machine and all of the connected filesystems,
it would require 166.8TB of storage, which would be prohibitively expensive
for capturing this one application alone.  Further, if multiple
similar applications are preserved, we would miss the opportunity to identify
common dependencies and store them once for multiple artifacts.
A more structured approach to dependency management is needed.

Figure~\ref{fig:version-evolution} shows how we have evolved this artifact
through several stages which make it more suitable for preservation.
In each step of evolution, we make the dependencies of the artifact
more explicit and available for analysis and automated processing.
As noted in the previous section, the original author provided us with
prose instructions by email which we translated into an
executable script.  The executable script has embedded in it
a number of external identifiers such as URLs pointing to repositories
and paths to networked filesystems.  As a general programming practice,
embedding such constants into the middle of a program is unwise, and so
we extract all of those identifiers and place them \emph{outside} the
script in a \emph{dependency map} or just \emph{map} for short.
The dependency map lists all of the external dependencies of the application, indicating
the type, how they are accessed, and where they are currently located.
The resulting script then simply refers to abstract file locations such
as \verb$GIT$ and \verb$CVMFS$, while the map file indicates where they
are currently located. If properly constructed, the script should not refer to any external
resource unless it is indicated in the dependency map.  We call this idealized
artifact an \emph{abstract script}.

By extracting the dependencies into the dependency map,
we introduce great freedom for the curator to move, transform, and otherwise
manipulate the dependencies of the artifact without damaging the artifact itself.
A Figure~\ref{fig:version-evolution} shows, it is straightforward for an
automated tool to examine
all of the dependencies in the map, download those that are missing,
and then modify the map to point to the local copies of the dependencies.
If we group the script, dependency map, and dependencies into a \emph{package},
we now have a self-contained artifact that can be moved from place to place.
In some cases, it may be safe to allow the dependency map to refer to 
trusted remote repositories.  Whether this is advisable is a judgment that
must be made by the user or the curator, taking into account the long-term
stability of said repositories.

However, only having the package and the dependency map is not enough. The successful execution of the application on the original machine also relies on the configuration of environment variables.
We collected the environment variables of the original machine and transformed it into one executable script. If another researcher wants to repeat the application, this executable script will be first executed. 
The environment variables refer to the dynamic named values defined in the range of one computer, like \verb!$PATH! and \verb!$PYTHONPATH!.
However, the dependency map refers to the actual storage location of path variables used in one abstract script. For example, the actual storage location of the path variable \verb!CVMFS! 
is {\tt /data/cvmfs/grid.cern.ch}.

\begin{figure}
\centering
\includegraphics[width=.5\textwidth]{solution3.eps}
\caption{Relationship of Roles}
\label{fig:solution3}
\end{figure}

The relationship of different roles involved in the application preservation and
reproduction is shown in Figure~\ref{fig:solution3}.  The original author uses the packaging utility to generate the package for one application.
Then the package, together with
its map file and description file will be published. When
another researcher wants to repeat the application, one copy of the package will be downloaded into the new machine and the application can be repeated.

When we try to repeat one application on one new machine, one map file is necessary for the relocation of the data access targets, as
show in Figure~\ref{fig:version-evolution}. 
The map file clearly defines the real location of each dependency in the format of dependency variables - the real location of dependency variable {\tt GIT} is \path{/data/git/cms-ttH} and the real location of dependency variable {\tt CVMFS}
is {\tt /data/cvmfs/grid.cern.ch}.
The script only refers to the dependency variables defined in the map file.
This design decouples the application script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
and ensures the transparent access.
The modification of the package only introduces the minimal changes of the map file on the client side.

This basic approach to dependency management is a step in the right direction
for dependencies that are \emph{explicit} and \emph{external} to the
user's native execution environment.  However, it leaves two other problems unsolved.

First, the basic approach requires that someone be \emph{aware} of the dependencies,
whether it be the end user, the system administrator, or the archive curator.
It seems reasonable to expect the user to be aware of a large dependency mentioned in a top-level script.
But, oftentimes the dependency is embedded invisibly deep within the software stack,
or is connected to the machine by the local system administrators.  No single party
is likely to have complete information about all of the dependencies.
Second, the basic approach assumes that the entire dependency is actually
consumed by the artifact.  As we have suggested above (and will show below),
this sort of program often only consumes a small fraction of what it does declare
as a dependency.

To address both of these problems, users and curators alike need tools that
will automatically observe the dependencies of complex applications, to
facilitate automatic and efficient preservation.

>>>>

\section{The Invariant Framework}

Given the challenges of reproducing HEP applications, we now describe components of a framework that must be present for other researchers to effectively reproduce the application. 
The framework consists of the following components (also shown in Figure \ref{}:

\begin{itemize}

\item {\bf Capture} In audit phase, PTU captures the execution of the application into a package. The resulting package contains the source code, its dependencies (system files, and files on network such as from CernVM-FS) and the data consumed and written by the application.

\item{\bf Preserve} The generated package is transferred to a Docker container of choice, instantiated from a vanilla, bare-bones image from a particular release (eg., CentOS 6.5, Fedora, or Ubuntu).  The container provides a base execution environment for the package. Now, the container with the package can be saved as a docker image.

\item {Distribute} The saved image can be stored and distributed in a repository like Docker Hub. We imagine these repositories would be preserved, and linked with a digital library.

 There are a number of other considerations: is it practical to store the data with the image? What if the “application” requires many processing cores to complete its task? Can one preserve the “DNA” of the application in one small, practical step, yet store everything needed for future reproductions? xHow do we minimize the complexity of the image repository (hub), stemming unnecessary growth and profitably curating the collection?

For purposes of preservation validation, a logical preservation unit (PLU) might be defined which consists of a minimal execution of the software using a small, test data sample, with specified outputs for comparison with future reproduction-validation runs.

A DASPOS preservation testing environment might consist of:

A collection of base images to be used when creating preserved platform-packages
A tool set that assists users in the 1+2+3 steps outlined above
A registry/repo service
A validation service consisting of a number of container slots that can be started on demand
A nightly testing service (Jenkins-like) that continuously monitors the reproducibility state of the preserved application + dependencies + environment + platform.

\end{itemize}

%\section{Evolving the Artifact}
%
%\begin{figure*}[t]
%\centering
%\includegraphics[width=.8\textwidth]{version-evolution.eps}
%\caption{Version Evolution}
%\label{fig:version-evolution}
%\end{figure*}
%
%It is clear that the artifact, as provided, is not in a suitable form
%for preservation.  While it might be technically possible to automatically
%capture the entire virtual machine and all of the connected filesystems,
%it would require 166.8TB of storage, which would be prohibitively expensive
%for capturing this one application alone.  Further, if multiple
%similar applications are preserved, we would miss the opportunity to identify
%common dependencies and store them once for multiple artifacts.
%A more structured approach to dependency management is needed.
%
%Figure~\ref{fig:version-evolution} shows how we have evolved this artifact
%through several stages which make it more suitable for preservation.
%In each step of evolution, we make the dependencies of the artifact
%more explicit and available for analysis and automated processing.
%As noted in the previous section, the original author provided us with
%prose instructions by email which we translated into an
%executable script.  The executable script has embedded in it
%a number of external identifiers such as URLs pointing to repositories
%and paths to networked filesystems.  As a general programming practice,
%embedding such constants into the middle of a program is unwise, and so
%we extract all of those identifiers and place them \emph{outside} the
%script in a \emph{dependency map} or just \emph{map} for short.
%The dependency map lists all of the external dependencies of the application, indicating
%the type, how they are accessed, and where they are currently located.
%The resulting script then simply refers to abstract file locations such
%as \verb$GIT$ and \verb$CVMFS$, while the map file indicates where they
%are currently located. If properly constructed, the script should not refer to any external
%resource unless it is indicated in the dependency map.  We call this idealized
%artifact an \emph{abstract script}.
%
%By extracting the dependencies into the dependency map,
%we introduce great freedom for the curator to move, transform, and otherwise
%manipulate the dependencies of the artifact without damaging the artifact itself.
%A Figure~\ref{fig:version-evolution} shows, it is straightforward for an
%automated tool to examine
%all of the dependencies in the map, download those that are missing,
%and then modify the map to point to the local copies of the dependencies.
%If we group the script, dependency map, and dependencies into a \emph{package},
%we now have a self-contained artifact that can be moved from place to place.
%In some cases, it may be safe to allow the dependency map to refer to 
%trusted remote repositories.  Whether this is advisable is a judgment that
%must be made by the user or the curator, taking into account the long-term
%stability of said repositories.
%
%However, only having the package and the dependency map is not enough. The successful execution of the application on the original machine also relies on the configuration of environment variables.
%We collected the environment variables of the original machine and transformed it into one executable script. If another researcher wants to repeat the application, this executable script will be first executed. 
%The environment variables refer to the dynamic named values defined in the range of one computer, like \verb!$PATH! and \verb!$PYTHONPATH!.
%However, the dependency map refers to the actual storage location of path variables used in one abstract script. For example, the actual storage location of the path variable \verb!CVMFS! 
%is {\tt /data/cvmfs/grid.cern.ch}.
%
%\begin{figure}
%\centering
%\includegraphics[width=.5\textwidth]{solution3.eps}
%\caption{Relationship of Roles}
%\label{fig:solution3}
%\end{figure}
%
%The relationship of different roles involved in the application preservation and
%reproduction is shown in Figure~\ref{fig:solution3}.  The original author uses the packaging utility to generate the package for one application.
%Then the package, together with
%its map file and description file will be published. When
%another researcher wants to repeat the application, one copy of the package will be downloaded into the new machine and the application can be repeated.
%
%When we try to repeat one application on one new machine, one map file is necessary for the relocation of the data access targets, as
%show in Figure~\ref{fig:version-evolution}. 
%The map file clearly defines the real location of each dependency in the format of dependency variables - the real location of dependency variable {\tt GIT} is \path{/data/git/cms-ttH} and the real location of dependency variable {\tt CVMFS}
%is {\tt /data/cvmfs/grid.cern.ch}.
%The script only refers to the dependency variables defined in the map file.
%This design decouples the application script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
%and ensures the transparent access.
%The modification of the package only introduces the minimal changes of the map file on the client side.
%
%This basic approach to dependency management is a step in the right direction
%for dependencies that are \emph{explicit} and \emph{external} to the
%user's native execution environment.  However, it leaves two other problems unsolved.
%
%First, the basic approach requires that someone be \emph{aware} of the dependencies,
%whether it be the end user, the system administrator, or the archive curator.
%It seems reasonable to expect the user to be aware of a large dependency mentioned in a top-level script.
%But, oftentimes the dependency is embedded invisibly deep within the software stack,
%or is connected to the machine by the local system administrators.  No single party
%is likely to have complete information about all of the dependencies.
%Second, the basic approach assumes that the entire dependency is actually
%consumed by the artifact.  As we have suggested above (and will show below),
%this sort of program often only consumes a small fraction of what it does declare
%as a dependency.
%
%To address both of these problems, users and curators alike need tools that
%will automatically observe the dependencies of complex applications, to
%facilitate automatic and efficient preservation.
%

### 2015-01-12 intro.tex
Major cleanup

-----
OLD TEXT

Reproducibility is a cornerstone of the scientific process~\cite{borgman2012data}.
In order to understand, verify, and build upon previous work,
one must be able to first recreate previous results by applying
the same methods. Historically, reproducibility has been
accomplished through painstaking detailed documentation recorded
in lab notebooks, which are then summarized in peer-reviewed publications.
But as science increasingly depends on computation,
reproducibility must also encompass the environments, data, and software
involved in each result~\cite{zabolitzky2002preserving}. It is widely recognized that informal
descriptions of software and systems -- although common -- are insufficient
for reproducing a computational result accurately.
A more automated and comprehensive approach is required.

The reproduction of a computation has three broad components,
each of which suggests somewhat different approaches:

\begin{itemize}
\item The {\bf computing environment}, consisting of the basic hardware and the operating system which can be preserved as physical artifacts or as a combination of virtual machine monitors (hardware) and virtual machine images (operating system)~\cite{matthews2009towards}.
\item The {\bf scientific data} to be analyzed has historically received the most attention for curation.  In a large, well-organized project, it may be stored in a  data repository or database management system, with associated documentation and a curation strategy.  In a small effort, it could simply be a handful of files.
\item The {\bf software environment} includes the source code, binaries, scripts, configuration files, and everything else needed to execute the desired code.  As with data, the software could be drawn from a well-managed software repository, or it could be a handful custom scripts that exist in the user's home directory.
\end{itemize}

In a very abstract sense, reproducing a computation is trivial.
Assuming a computation is deterministic, one must simply
preserve all of the inputs to a computation, then re-run
the same code in an equivalent environment, and the same result
will be produced.  For a small custom application on a modest
amount of data, this could be accomplished by capturing the
complete environment,
data, and software within a single virtual machine image,
and then depositing the virtual
image into a curated environment.  The publication could
then simply refer to the identifier of the image, which the
interested reader can obtain and re-use. This approach has
been used to some success with systems~\cite{castagne2013consider}.
\footnote{Of course, we are glossing over the problem that hardware
architectures and virtual machines also change, so one must also
preserve the VMM software necessary to run the image.  The VMM itself
depends on a software environment which must also be preserved.
A long-term preservation system might end up running a whole
stack of nested virtual machines in order to provide the desired
environment! }

However, this simple approach is not sufficient for large applications
that are run in complex environments.

\begin{itemize}
\item There may be {\bf implicit dependencies} on items that are
not apparent to the end user.  For example, they may understand that
they rely on a particular data analysis package, but would have
no reason to know that the package has further dependencies on
other libraries and configuration files.  Or, they may know that
the computation only runs correctly on a particular machine, but
not know this is because it relies on a filesystem that
is mounted only on that machine.

\item The {\bf granularity} of the dependencies may not be well understood.
For example, the user may understand that a computation depends upon
a data collection that is 1TB in overall size, but not have detailed
knowledge that it only requires three files totalling 300MB out of that
whole collection.

\item There may be dependencies upon {\bf networked resources} that
are inherently external to the system, such as a database, a code
repository~\cite{cms2006cmssw}, or a scalable filesystem~\cite{blomer2011cernvm}.  For such resources, it
must be decided whether the dependency will simply be noted, or if it
must be incorporated whole or in part.

\item Where {\bf common dependencies} are widely used, it may be inefficient or
impossible to store one copy of each dependency for each archived object.
Some form of sharing or de-duplication is necessary in order to keep
the archive to a reasonable size.
\end{itemize}

We do not claim to have solved these problems in any comprehensive
way.  Rather, our aim in this paper is to highlight the scope
of the problems by presenting a case study of one complex application.
The application is presented to us
first in the form of an email that describes in prose how to install
the software and run the analysis.  We perform several successive
refinements to convert it into an executable and preservable object.
We then develop techniques for reducing the size of the dependencies
that are necessary for the object to function, and we demonstrate
the preserved object functioning correctly in three different
physical and cloud environments.
We describe how each of these techniques may interact with
a future archive of preserved software artifacts, and conclude with
some reflections on the challenges of preservation and advice for future efforts.

>>>>

%-----
%OLD TEXT
%
%Reproducibility is a cornerstone of the scientific process~\cite{borgman2012data}.
%In order to understand, verify, and build upon previous work,
%one must be able to first recreate previous results by applying
%the same methods. Historically, reproducibility has been
%accomplished through painstaking detailed documentation recorded
%in lab notebooks, which are then summarized in peer-reviewed publications.
%But as science increasingly depends on computation,
%reproducibility must also encompass the environments, data, and software
%involved in each result~\cite{zabolitzky2002preserving}. It is widely recognized that informal
%descriptions of software and systems -- although common -- are insufficient
%for reproducing a computational result accurately.
%A more automated and comprehensive approach is required.
%
%The reproduction of a computation has three broad components,
%each of which suggests somewhat different approaches:
%
%\begin{itemize}
%\item The {\bf computing environment}, consisting of the basic hardware and the operating system which can be preserved as physical artifacts or as a combination of virtual machine monitors (hardware) and virtual machine images (operating system)~\cite{matthews2009towards}.
%\item The {\bf scientific data} to be analyzed has historically received the most attention for curation.  In a large, well-organized project, it may be stored in a  data repository or database management system, with associated documentation and a curation strategy.  In a small effort, it could simply be a handful of files.
%\item The {\bf software environment} includes the source code, binaries, scripts, configuration files, and everything else needed to execute the desired code.  As with data, the software could be drawn from a well-managed software repository, or it could be a handful custom scripts that exist in the user's home directory.
%\end{itemize}
%
%In a very abstract sense, reproducing a computation is trivial.
%Assuming a computation is deterministic, one must simply
%preserve all of the inputs to a computation, then re-run
%the same code in an equivalent environment, and the same result
%will be produced.  For a small custom application on a modest
%amount of data, this could be accomplished by capturing the
%complete environment,
%data, and software within a single virtual machine image,
%and then depositing the virtual
%image into a curated environment.  The publication could
%then simply refer to the identifier of the image, which the
%interested reader can obtain and re-use. This approach has
%been used to some success with systems~\cite{castagne2013consider}.
%\footnote{Of course, we are glossing over the problem that hardware
%architectures and virtual machines also change, so one must also
%preserve the VMM software necessary to run the image.  The VMM itself
%depends on a software environment which must also be preserved.
%A long-term preservation system might end up running a whole
%stack of nested virtual machines in order to provide the desired
%environment! }
%
%However, this simple approach is not sufficient for large applications
%that are run in complex environments.
%
%\begin{itemize}
%\item There may be {\bf implicit dependencies} on items that are
%not apparent to the end user.  For example, they may understand that
%they rely on a particular data analysis package, but would have
%no reason to know that the package has further dependencies on
%other libraries and configuration files.  Or, they may know that
%the computation only runs correctly on a particular machine, but
%not know this is because it relies on a filesystem that
%is mounted only on that machine.
%
%\item The {\bf granularity} of the dependencies may not be well understood.
%For example, the user may understand that a computation depends upon
%a data collection that is 1TB in overall size, but not have detailed
%knowledge that it only requires three files totalling 300MB out of that
%whole collection.
%
%\item There may be dependencies upon {\bf networked resources} that
%are inherently external to the system, such as a database, a code
%repository~\cite{cms2006cmssw}, or a scalable filesystem~\cite{blomer2011cernvm}.  For such resources, it
%must be decided whether the dependency will simply be noted, or if it
%must be incorporated whole or in part.
%
%\item Where {\bf common dependencies} are widely used, it may be inefficient or
%impossible to store one copy of each dependency for each archived object.
%Some form of sharing or de-duplication is necessary in order to keep
%the archive to a reasonable size.
%\end{itemize}
%
%We do not claim to have solved these problems in any comprehensive
%way.  Rather, our aim in this paper is to highlight the scope
%of the problems by presenting a case study of one complex application.
%The application is presented to us
%first in the form of an email that describes in prose how to install
%the software and run the analysis.  We perform several successive
%refinements to convert it into an executable and preservable object.
%We then develop techniques for reducing the size of the dependencies
%that are necessary for the object to function, and we demonstrate
%the preserved object functioning correctly in three different
%physical and cloud environments.
%We describe how each of these techniques may interact with
%a future archive of preserved software artifacts, and conclude with
%some reflections on the challenges of preservation and advice for future efforts.

### 2015-01-12 measure.tex
Major cleanup

@@

\subsection{Tracking of Network Dependencies}

\begin{figure}
\centering
\includegraphics[width=.6\textwidth]{git-syscall.eps}
\caption{Exec Syscalls of a git command}
\label{fig:git-syscall}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.6\textwidth]{http_packet.eps}
\caption{HTTP Request and Response}
\label{fig:http_packet}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.6\textwidth]{url_redirection.eps}
\caption{An Example of URL Redirection}
\label{fig:url_redirection}
\end{figure}

All the dependencies of one program can be divided into three categories: local file system (e.g., /usr, /lib and /lib64), remote file systems which can be mounted as local directories (e.g., /cvmfs and /hdfs), and other remote network dependencies (e.g. http, https and ssh).
Through utilizing ptrace to trap each file-relevant system call used by a program, the first two categories of dependencies can be collected. 
Motivation of tracking network dependencies: Linkrot is a common and great threat to the preservation of scientific applications. A URL which works normally today may be unavailable permanently. A method which can help the scientists figure out all the network dependencies of their applications provides the chance to evaluate the stability of each network dependencies and preserve the unstable network resources before linkrot happens.
One direct solution to track the third category of dependencies is to utilize ptrace to check each exec system call used by a program and record each network-relevant executable and its parameters. However, an executable may create one or more child processes to finish some tasks, and a child process may create their own children processes. Figure~\ref{fig:git-syscall} shows all the processes created by a git command. A process with PID 998 is created to clone a remote git repository into local machine, which totally has 6 child processes. Moreover, a network-relevant executable name collection is necessary to identify network dependencies. The diversity of network-relevant executables and the large process tree generated for a network executable make this solution infeasible.

Another solution to track network dependencies is to track the network sockets. The user process communicates with the network protocol stacks in the kernel through the network socket layer user interface on Linux. From the process tree shown in the above figure, the process with PID 1000 responds to create a socket, connect to a DNS server, send a DNS request packet to the DNS server and receive a DNS response packet from the DNS server. The information gained from the network socket tracking can be divided into three categories.
\begin{itemize}
\item The information of network sockets used to communicate with remote network dependences (through socket and connect system calls) can be used to figure out the port number, service name (such as, http, https, and ssh), socket type (stream and datagram),  and the domain type (inet and inet6). 
\item The contents of DNS packets can be used to figure out the hostname and IP address of each remote network dependency. 
\item As for applications based on http protocol, all the http requests and responses can be seen, as shown in Figure~\ref{fig:http_packet}. However, as for applications based on https and ssh which encrypt network data using TLS/SSL, tracking network data on the socket level can only see the encrypted data. 
\end{itemize}

The results of tracking network sockets used by a program involves two categories of network resource redirections, dns-level hostname redirection and website-level url redirection. 
\begin{itemize}
\item dns-level hostname redirection: Each DNS packet includes five parts, header, question, answer, authority, and additional. A DNS response packet with the type CNAME has multiple answers. For example, the DNS response packet which tries to resolve {\tt www3.nd.edu} includes two answers. The first answer provides an alias of {\tt www3.nd.edu}, {\tt www-vip.cc.nd.edu}, and the second answer maps the alias to the IP address. 
{\tt www3.nd.edu} CNAME {\tt www-vip.cc.nd.edu}
{\tt www-vip.cc.nd.edu} A {\tt 129.74.12.151}
The CNAME-type DNS packets leave us a question, among the hostname used by the user, the alias(es), the IP address, what should we preserve?
\item website-level url redirection: Website-level url redirection happens when a website updates its location and still want their old users access their resources using the old url. Figure~\ref{fig:url_redirection} illustrates the url redirection between {\tt \url{www3.nd.edu/~ccl}} and {\tt ccl.cse.nd.edu}. Except for the difference of hostnames, the application layer protocols used by the old-version website and the new-version website is also different: the old website provides services through the https protocol, while the new website provides services through the http protocol. 
\end{itemize}

The usage of https protocol makes detecting of website-level url redirections through tracking system calls more difficulty and even impossible. All the application data will be encrypted at presentation layer through the TLS/SSL protocol, which is initialized at the session layer and works at the presentation layer.

>>>>

\section{Component Tools for Reproducible Research}

@@

%\subsection{Tracking of Network Dependencies}
%
%\begin{figure}
%\centering
%\includegraphics[width=.6\textwidth]{git-syscall.eps}
%\caption{Exec Syscalls of a git command}
%\label{fig:git-syscall}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics[width=.6\textwidth]{http_packet.eps}
%\caption{HTTP Request and Response}
%\label{fig:http_packet}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics[width=.6\textwidth]{url_redirection.eps}
%\caption{An Example of URL Redirection}
%\label{fig:url_redirection}
%\end{figure}
%
%All the dependencies of one program can be divided into three categories: local file system (e.g., /usr, /lib and /lib64), remote file systems which can be mounted as local directories (e.g., /cvmfs and /hdfs), and other remote network dependencies (e.g. http, https and ssh).
%Through utilizing ptrace to trap each file-relevant system call used by a program, the first two categories of dependencies can be collected. 
%Motivation of tracking network dependencies: Linkrot is a common and great threat to the preservation of scientific applications. A URL which works normally today may be unavailable permanently. A method which can help the scientists figure out all the network dependencies of their applications provides the chance to evaluate the stability of each network dependencies and preserve the unstable network resources before linkrot happens.
%One direct solution to track the third category of dependencies is to utilize ptrace to check each exec system call used by a program and record each network-relevant executable and its parameters. However, an executable may create one or more child processes to finish some tasks, and a child process may create their own children processes. Figure~\ref{fig:git-syscall} shows all the processes created by a git command. A process with PID 998 is created to clone a remote git repository into local machine, which totally has 6 child processes. Moreover, a network-relevant executable name collection is necessary to identify network dependencies. The diversity of network-relevant executables and the large process tree generated for a network executable make this solution infeasible.
%
%Another solution to track network dependencies is to track the network sockets. The user process communicates with the network protocol stacks in the kernel through the network socket layer user interface on Linux. From the process tree shown in the above figure, the process with PID 1000 responds to create a socket, connect to a DNS server, send a DNS request packet to the DNS server and receive a DNS response packet from the DNS server. The information gained from the network socket tracking can be divided into three categories.
%\begin{itemize}
%\item The information of network sockets used to communicate with remote network dependences (through socket and connect system calls) can be used to figure out the port number, service name (such as, http, https, and ssh), socket type (stream and datagram),  and the domain type (inet and inet6). 
%\item The contents of DNS packets can be used to figure out the hostname and IP address of each remote network dependency. 
%\item As for applications based on http protocol, all the http requests and responses can be seen, as shown in Figure~\ref{fig:http_packet}. However, as for applications based on https and ssh which encrypt network data using TLS/SSL, tracking network data on the socket level can only see the encrypted data. 
%\end{itemize}
%
%The results of tracking network sockets used by a program involves two categories of network resource redirections, dns-level hostname redirection and website-level url redirection. 
%\begin{itemize}
%\item dns-level hostname redirection: Each DNS packet includes five parts, header, question, answer, authority, and additional. A DNS response packet with the type CNAME has multiple answers. For example, the DNS response packet which tries to resolve {\tt www3.nd.edu} includes two answers. The first answer provides an alias of {\tt www3.nd.edu}, {\tt www-vip.cc.nd.edu}, and the second answer maps the alias to the IP address. 
%{\tt www3.nd.edu} CNAME {\tt www-vip.cc.nd.edu}
%{\tt www-vip.cc.nd.edu} A {\tt 129.74.12.151}
%The CNAME-type DNS packets leave us a question, among the hostname used by the user, the alias(es), the IP address, what should we preserve?
%\item website-level url redirection: Website-level url redirection happens when a website updates its location and still want their old users access their resources using the old url. Figure~\ref{fig:url_redirection} illustrates the url redirection between {\tt \url{www3.nd.edu/~ccl}} and {\tt ccl.cse.nd.edu}. Except for the difference of hostnames, the application layer protocols used by the old-version website and the new-version website is also different: the old website provides services through the https protocol, while the new website provides services through the http protocol. 
%\end{itemize}
%
%The usage of https protocol makes detecting of website-level url redirections through tracking system calls more difficulty and even impossible. All the application data will be encrypted at presentation layer through the TLS/SSL protocol, which is initialized at the session layer and works at the presentation layer.
